---
title: "viewTrial"
author: 
- Suvitha Subramaniam
- Katharina Klatte
date: "4/25/2022"
output: pdf_document
toc: true ## Table of contents
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

# Introduction

The R package, viewTrial, is a minimal version of a R shiny web application for centralized monitoring in clinical trials. 

# Structure 

* The R Shiny app is developed in a modular fashion as an R package
* Functions required to run the app are in the /R directory. 

This vignette will guide you in adapting the template to create your own R Shiny dashboard for centralized monitoring. 

# Installing

The package can be directly installed from [\textcolor{blue}{GitHub}] (https://github.com/suvi-subra/viewTrial). You will need to have the R package 'devtools' installed for this.

```{r, eval = FALSE}

devtools::install_github("suvi-subra/viewTrial")

```

To run the app locally on your computer after installation, run

```{r, eval = FALSE}

library(viewTrial)
run_app()

```

# Adapting the template

1. Renaming the package

Change the name of the package in the DESCRIPTION file.

2. Loading data: R/get_data.R

In this script, raw data is loaded and processed to be used in the app. The processed data is returned as a list of named dataframes. 

3. Getting reactive data: R/get_reactive.R

4. Module aliases: R/get_modules.R

5. UI: R/ui.R

6. Server: R/server.R

7. Bring it all together: R/run_app.R

\newpage

# Extending the app

For example, let's add a tab named "Home" to the existing app. 

1. Create a new R file named R/mod_home.R by copying and renaming R/mod_skeleton.R.

2. Add the line home = "mod_home" to list of module aliases in R/get_modules.R.

3. Add the line menuItem("Home", tabName = mod$home, icon = icon("home")) to R/ui.R. You can choose an icon from https://fontawesome.com/icons and https://getbootstrap.com/docs/3.3/components/#glyphicons.

4. Add ui and server content in R/mod_home.R

5. Call module in R/server.R by adding this line callModule(mod_home_server, mod$home).

# Disclaimer

# sessionInfo()

```{r}

sessionInfo()

```

